The effects of varying depth in cosmic shear surveys

### 2019-11-19 Heydenreich_et_al.tex
added referee comments
added catherine's suggestion

\usepackage{bm}
\usepackage{verbatim}
\usepackage{xcolor}
%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
% \usepackage{subcaption}
%\usepackage{hyperref}

@@

{\bf So far the effects of varying depth have not been extensively studied: \citet{Guzik:2005} investigate the effect of a general, position-dependent multiplicative shear bias on the shear power spectrum through simulations, but do not perform a quantitative analysis. Furthermore, varying depth was one of the effects included in mock catalogs in the Subaru Hyper Suprime-Cam Survey \citep{Shirasaki:2019}, but they did not discuss its implications in detail.
}

>>>>

\usepackage{bm}
\usepackage{verbatim}
\usepackage{xcolor}
%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage[section]{placeins}
% \usepackage{subcaption}
%\usepackage{hyperref}

@@

{\bf This work is complementary to the analysis of \citet{Guzik:2005} who investigate the effect of a general, position-dependent multiplicative shear bias on the shear power spectrum.  In principle the varying depth of the source galaxy sample that we study here could be recast as a varying effective shear bias.  The inclusion of an inhomogeneous distribution of source galaxies has also been explored using mock catalogs of the Subaru Hyper Suprime-Cam Survey \citep{Shirasaki:2019}, with a focus on resulting estimation of the cosmic shear covariance matrix.

}
